---
title: "OW Performance Charts"
output:
  flexdashboard::flex_dashboard:
    css: www/styles.css
    vertical_layout: scroll
    orientation: rows
runtime: shiny
resource_files:
- "data-ready/Reporting Quarters.xlsx"
- "data-ready/Targets.xlsx"
- "data-ready/wips_variables.csv"
- "data-ready/combined_QPR_ow_data.csv"
- "scripts-dashboards/01_load_data_ow.R"
- "scripts-dashboards/02_functions.R"
- "scripts-dashboards/03_for_all_grantee_charts.R"
- "scripts-dashboards/functions.R"
- "ow_pdf_by_grantee.Rmd"

---

```{r libraries, include=FALSE}

library(tidyverse)
library(lubridate)
library(knitr)
library(scales)
library(janitor)
library(here)
library(ggiraph)
library(plotly)
library(shiny)
library(shinydashboard)
library(kableExtra)
library(htmltools)
library(rmarkdown)

```

```{r setup, include=FALSE}

source(here("scripts-dashboards", "01_load_data_ow.R"))
source(here("scripts-dashboards", "02_functions.R"))
source(here("scripts-dashboards", "03_for_all_grantee_charts.R"))



```

```{r functions, include=FALSE}

silly_legend <- reactive({
  
show_columns <<- df_grant_years %>%
  filter(Year %in% input$years) %>%
  mutate(Year = 1) %>%
  group_by(Year) %>%
  mutate(columns = paste0(`Reporting Quarters`, collapse = "|")) %>%
  ungroup() %>%
  select(columns) %>% 
  distinct() %>%
  pull()


targets_viewed <<- for_make_table_all %>%
    select(matches(show_columns)) %>%
    select(matches("Target$"))

quarters <- for_make_table_all %>%
    select(matches(show_columns)) %>%
    select(matches("[0-9]{2}.[0-9]{2}.[0-9]{4}$"))

just_qtrs <<- quarters %>% colnames()
first_quarter <<- first(just_qtrs)
last_quarter <<- last(just_qtrs)
header_targets <<- ncol(targets_viewed)
header_quarters <<- ncol(quarters)
first_qtr <<- first(quarters)
last_qtr <<- last(quarters)
last_qtr_col <<- quarters %>% select(last_col(0L)) %>% colnames() %>% stringr::str_extract("^[0-9]{2}.[0-9]{2}")
last_qtr_column <<- quarters %>% select(last_col(0L)) %>% colnames() %>% sym()
current_reporting_year <<- df_grant_years_raw |> 
  mutate(
    reporting_qtr_format = format(`Reporting Quarters`, "%m.%d.%Y")
  ) |>
  filter(
    reporting_qtr_format == last_quarter
  )
previous_reporting_year <<-
  df_grant_years |> ungroup() |> mutate(previous_year = lag(Year)) |> filter(Year == current_reporting_year$Year) |> pull(previous_year)
previous_reporting_quarter <<-
  df_grant_years_raw[df_grant_years_raw$Year == previous_reporting_year,] |> select(3) |> slice_head() |> pull() |> format("%m.%d.%Y")


  current_threshold <<- threshold_guide %>%
  filter(quarter == last_qtr_col) #current_qtr
})
  
  t_green <- reactive({seq(current_threshold$green_b, current_threshold$green_t, by = .01) %>% percent(accuracy = 1)})
  t_yellow <- reactive({seq(current_threshold$yellow_b, current_threshold$yellow_t, by = .01) %>% percent(accuracy = 1)})
  t_red <- reactive({seq(0, current_threshold$red_t, by = .01) %>% percent(accuracy = 1)})

# reactivity for by grantee tab
by_grantee_listener <- reactive({
  
    plotnum <<- as.numeric(input$grantee)
  headername <<- choices_rev[[plotnum]]
  currenttable <<- table_by_grantee_no_kbl[[plotnum]]
  
  
  beg_qtr <<- input$startdate %>% as.Date("%Y-%m-%d") %>% format("%m.%d.%Y") %>% sym()
  end_qtr <<- input$enddate %>% as.Date("%Y-%m-%d") %>% format("%m.%d.%Y") %>% sym()
  
  qtr_count <<- currenttable %>% 
    select(beg_qtr:end_qtr) %>% 
    ncol()
  
  quarters_selected <<- currenttable %>% 
    select(any_of(beg_qtr):any_of(end_qtr)) %>% colnames()
  
  targets_selected <<- tibble(targets_for_table_by_grantee) %>%
    slice(input$targets_by_grantee[1]:input$targets_by_grantee[2]) %>% 
    pull()
  
  targets_count <<- length(targets_selected)
  
    
  better_by_grantee_table <<- currenttable %>%
    select(
      `Performance Metric`,
      beg_qtr:end_qtr, 
      all_of(targets_selected),
      `Total Target`,
      previous_year_target_met,
      is_6_30_qtr) %>%
    rowwise() %>% 
    mutate(
      `Cumulative Target` = sum(c_across(targets_selected)),
      `% of Cumulative Target` = scales::percent(!!end_qtr/`Cumulative Target`),
      .before = `Total Target`
      ) %>% 
    mutate(
      `% of Total Target` = scales::percent(!!end_qtr/`Total Target`), .after = `Total Target`
    )
  
  totalcols <<- qtr_count + targets_count + 3
  
  
  end_qtr_threshold <- rlang::as_string(end_qtr) %>% stringr::str_extract("^[0-9]{2}.[0-9]{2}")
  current_threshold_by_grantee <<- threshold_guide %>%
    filter(quarter == end_qtr_threshold) #current_qtr

})

```


All Grantees
=====================================
Inputs {.sidebar}
-------------------------------------

```{r}
checkboxGroupInput(
  "years", 
  "Reporting Years",
  selected = c("1", "2", "3", "4"),
  inline = FALSE,
  choiceNames = c("Y1", "Y2", "Y3", "Y4", "Extension"),
  choiceValues = c("1", "2", "3", "4", "Extension")
  )

# VALUES FOR TABLES -------------------------------



# THRESHOLDS LEGEND ------------------------



renderUI({
  # print(input$years)
  silly_legend()
  
  htmltools::tagList(
  tags$div(class = "legend", 
           tags$span(id = "legend-label", "Quarterly Thresholds Key"),
           tags$table(id = "legendid",
             tags$tr(
               tags$th(colspan = 2, paste0(current_threshold$quarter, " Quarterly Threshold"))
             ),
             tags$tr(
               tags$td(
                 div(id = "lightgreen")
               ),
               tags$td(class = "legendtext",
                       paste0(current_threshold$nice_green_b, " or above")
               )
             ),
             tags$tr(
               tags$td(
                 div(id = "yellow")
               ),
               tags$td(class = "legendtext",
                       paste0("Between ", current_threshold$nice_yellow_b, " to ", current_threshold$nice_yellow_t)
               )
             ),
             tags$tr(
               tags$td(
                 div(id = "lightpink")
               ),
               tags$td(class = "legendtext",
                       paste0(current_threshold$nice_red_t, " or below")
               )
             )
           )
  )
)
  
})
```


Row {data-height=450}
------------------------------------
### Summary


```{r}

renderUI({

  silly_legend()
  
  table_all_grantees <- for_make_table_all %>%
  select(
    `Performance Metric`,
    matches(show_columns),
    `% of Cumulative Target*` = `% of Current Year Target*`,
    `Total Target`,
    `% of Total Target`
    ) %>%
    rowwise() %>% 
    mutate(
      `Cumulative Target` = sum(c_across(colnames(targets_viewed))),
      .before = `% of Cumulative Target*`
    ) %>%
    mutate(
      `% of Cumulative Target*` = scales::percent(!!last_qtr_column/`Cumulative Target`) #https://rlang.r-lib.org/reference/topic-inject.html
    ) %>%
  kbl_table() %>% 
  scroll_box(width = "900px", height = "100%") |> 
  add_header_above(c(" " = 1,
                     "Reporting Quarters" = header_quarters,
                     "Targets" = header_targets+2,
                     "Progress to Targets" = 2))
current_year_color <- 1+header_quarters+header_targets+2
  
  HTML(
    table_all_grantees %>%
      column_spec(1, width_min = '3in') %>%
      column_spec(
        current_year_color,
        width_min = '70px',
        width_max = '75px',
        background = case_when(
          for_make_table_all$`% of Current Year Target*` %in% t_yellow() & for_make_table_all$is_6_30_qtr == 1 & for_make_table_all$previous_year_target_met == 0 ~ "lightpink",
          for_make_table_all$`% of Current Year Target*` %in% t_green() ~ "lightgreen",
          for_make_table_all$`% of Current Year Target*` %in% t_yellow() ~ "yellow",
          for_make_table_all$`% of Current Year Target*` %in% t_red() ~ "lightpink",
          TRUE ~ "white"),
        extra_css = "border-radius: 4px;")
  )
})
```


::: {.footnote}
*% of Current Year Target calculated as most recently available quarterly data divided by sum of cumulative milestones-to-date. e.g. Year 2 milestone is sum of Year 1 & Year 2 annual milestones.
:::


Row {.tabset .tabset-fade}
-------------------------------------
### Total Participants Served
```{r}
renderPlot({
  
  silly_legend()

  all_grantees$tps_ps +
          scale_x_date(limits = c(as.Date(first_quarter, "%m.%d.%Y"), as.Date(last_quarter, "%m.%d.%Y")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(just_qtrs, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
  
  })
```

### Progress to Current Year Target
```{r}

participants_served <- reactive({
  
    silly_legend()

    yellow_green_participants_served <- readr::parse_number(t_green()) %>% first()
  red_yellow_participants_served <- readr::parse_number(t_yellow()) %>% first()
  
  master_table_grantees %>%
    filter(`Performance Metric` == "Total Participants Served") %>%
    rowwise() %>%
    mutate(
      `Cumulative Target` = sum(c_across(str_replace_all(colnames(targets_viewed), "<br>", "\n"))),
      `% of Cumulative Target` = (!!last_qtr_column/`Cumulative Target`*100)
    ) %>%
    mutate(`% of Cumulative Target*` = percent(`% of Cumulative Target`/100, accuracy = 1)) %>%
    rowwise() %>% 
  mutate(color_bars = case_when(
    `% of Cumulative Target` < yellow_green_participants_served &
      `% of Cumulative Target` > red_yellow_participants_served & is_6_30_qtr == 1 & previous_year_target_met == 0 ~ "#FF9B9B",
    `% of Cumulative Target` >= yellow_green_participants_served ~ "#70AD47",
    `% of Cumulative Target` < yellow_green_participants_served &
      `% of Cumulative Target` > red_yellow_participants_served ~ "#FFFF00",
    `% of Cumulative Target` <= red_yellow_participants_served ~ "#FF9B9B",
    TRUE ~ "lightgray"
  )) |> 
          select(
      `Grantee Name`,
      `% of Cumulative Target`,
      `% of Cumulative Target*`,
      color_bars
    ) %>%
    arrange(desc(`% of Cumulative Target`))
})

renderPlot({

  chart_by_current_target(participants_served(), "Total Participants Served")

})

```


Row {.tabset .tabset-fade}
-------------------------------------
### Began Training
```{r}
renderPlot({
  
  silly_legend()

  all_grantees$train_bt +
          scale_x_date(limits = c(as.Date(first_quarter, "%m.%d.%Y"), as.Date(last_quarter, "%m.%d.%Y")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(just_qtrs, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
    })
```

### Progress to Current Year Target
```{r}


began_training <- reactive({
  
    silly_legend()

    yellow_green_began_training <- readr::parse_number(t_green()) %>% first()
  red_yellow_began_training <- readr::parse_number(t_yellow()) %>% first()
  
  master_table_grantees %>%
    filter(`Performance Metric` == "Participants Began Ed/Job Training") %>%
    rowwise() %>%
    mutate(
      `Cumulative Target` = sum(c_across(str_replace_all(colnames(targets_viewed), "<br>", "\n"))),
      `% of Cumulative Target` = (!!last_qtr_column/`Cumulative Target`*100)
    ) %>%
    mutate(`% of Cumulative Target*` = percent(`% of Cumulative Target`/100, accuracy = 1)) %>%
    rowwise() %>% 
  mutate(color_bars = case_when(
                   `% of Cumulative Target` < yellow_green_began_training &
      `% of Cumulative Target` > red_yellow_began_training & is_6_30_qtr == 1 & previous_year_target_met == 0 ~ "#FF9B9B",
    `% of Cumulative Target` >= yellow_green_began_training ~ "#70AD47",
    `% of Cumulative Target` < yellow_green_began_training &
      `% of Cumulative Target` > red_yellow_began_training ~ "#FFFF00",
    `% of Cumulative Target` <= red_yellow_began_training ~ "#FF9B9B",
    TRUE ~ "lightgray"
  )) |> 
     select(
      `Grantee Name`,
      `% of Cumulative Target`,
      `% of Cumulative Target*`,
      color_bars
    ) %>%
    arrange(desc(`% of Cumulative Target`))
})

renderPlot({
  
   chart_by_current_target(began_training(), "Participants Began Ed/Job Training") +
            scale_y_discrete(expand = expansion(mult = c(0, .3)))


})

```


Row {.tabset .tabset-fade}
-------------------------------------
### Completed Training
```{r}
renderPlot({
  
    silly_legend()
      
    all_grantees$train_ct +
          scale_x_date(limits = c(as.Date(first_quarter, "%m.%d.%Y"), as.Date(last_quarter, "%m.%d.%Y")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(just_qtrs, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
    })
```

### Progress to Current Year Target
```{r}

completed_training <- reactive({
  
    silly_legend()

    yellow_green_completed_training <- readr::parse_number(t_green()) %>% first()
  red_yellow_completed_training <- readr::parse_number(t_yellow()) %>% first()
  
  master_table_grantees %>%
    filter(`Performance Metric` == "Participants Completed Training") %>%
    rowwise() %>%
    mutate(
      `Cumulative Target` = sum(c_across(str_replace_all(colnames(targets_viewed), "<br>", "\n"))),
      `% of Cumulative Target` = (!!last_qtr_column/`Cumulative Target`*100)
    ) %>%

    mutate(`% of Cumulative Target*` = percent(`% of Cumulative Target`/100, accuracy = 1)) %>%
    rowwise() %>% 
  mutate(color_bars = case_when(
               `% of Cumulative Target` < yellow_green_completed_training &
      `% of Cumulative Target` > red_yellow_completed_training & is_6_30_qtr == 1 & previous_year_target_met == 0 ~ "#FF9B9B",
    `% of Cumulative Target` >= yellow_green_completed_training ~ "#70AD47",
    `% of Cumulative Target` < yellow_green_completed_training &
      `% of Cumulative Target` > red_yellow_completed_training ~ "#FFFF00",
    `% of Cumulative Target` <= red_yellow_completed_training ~ "#FF9B9B",
    TRUE ~ "lightgray"
  )) |> 
     select(
      `Grantee Name`,
      `% of Cumulative Target`,
      `% of Cumulative Target*`,
      color_bars
    ) %>%
    arrange(desc(`% of Cumulative Target`))
})

renderPlot({
  
   chart_by_current_target(completed_training(), "Participants Completed Training") +
    ylim(NA, max(completed_training()$`% of Cumulative Target`)*1.2)

})


```

 
Row {.tabset .tabset-fade}
-------------------------------------
### Completed with Credential
```{r}
renderPlot({
  
  silly_legend()

    all_grantees$train_cred_coc +
          scale_x_date(limits = c(as.Date(first_quarter, "%m.%d.%Y"), as.Date(last_quarter, "%m.%d.%Y")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(just_qtrs, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
    })
```

### Progress to Current Year Target
```{r}

completed_with_credential <- reactive({
  
    silly_legend()

    yellow_green_completed_with_credential <- readr::parse_number(t_green()) %>% first()
  red_yellow_completed_with_credential <- readr::parse_number(t_yellow()) %>% first()
  
  master_table_grantees %>%
    filter(`Performance Metric` == "Total Participants Completed and Obtained Credential") %>%
    rowwise() %>%
    mutate(
      `Cumulative Target` = sum(c_across(str_replace_all(colnames(targets_viewed), "<br>", "\n"))),
      `% of Cumulative Target` = (!!last_qtr_column/`Cumulative Target`*100)
    ) %>%
  
    mutate(`% of Cumulative Target*` = percent(`% of Cumulative Target`/100, accuracy = 1)) %>%
    rowwise() %>% 
  mutate(color_bars = case_when(
                 `% of Cumulative Target` < yellow_green_completed_with_credential &
      `% of Cumulative Target` > red_yellow_completed_with_credential & is_6_30_qtr == 1 & previous_year_target_met == 0 ~ "#FF9B9B",
    `% of Cumulative Target` >= yellow_green_completed_with_credential ~ "#70AD47",
    `% of Cumulative Target` < yellow_green_completed_with_credential &
      `% of Cumulative Target` > red_yellow_completed_with_credential ~ "#FFFF00",
    `% of Cumulative Target` <= red_yellow_completed_with_credential ~ "#FF9B9B",
    TRUE ~ "lightgray"
  )) |> 
     select(
      `Grantee Name`,
      `% of Cumulative Target`,
      `% of Cumulative Target*`,
      color_bars
    ) %>%
    arrange(desc(`% of Cumulative Target`))
})

renderPlot({
  
     chart_by_current_target(completed_with_credential(), "Total Participants Completed and Obtained Credential") +
    ylim(NA, max(completed_with_credential()$`% of Cumulative Target`)*1.2)
  
})

```



Row {.tabset .tabset-fade}
-------------------------------------
### Entered Employment
```{r}
renderPlot({
  
  silly_legend()
  
  all_grantees$empl_ee +
    scale_x_date(limits = c(as.Date(first_quarter, "%m.%d.%Y"), as.Date(last_quarter, "%m.%d.%Y")),
      date_labels = "%m.%d.%Y",
      breaks = as.Date(just_qtrs, "%m.%d.%Y"),
      expand = expansion(mult = 0.2)
    )+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
  })
```

### Progress to Current Year Target
```{r}

entered_employment <- reactive({
  
    silly_legend()

    yellow_green_entered_employment <- readr::parse_number(t_green()) %>% first()
  red_yellow_entered_employment <- readr::parse_number(t_yellow()) %>% first()
  
  master_table_grantees %>%
    filter(`Performance Metric` == "Entered Employment") %>%
    rowwise() %>%
    mutate(
      `Cumulative Target` = sum(c_across(str_replace_all(colnames(targets_viewed), "<br>", "\n"))),
      `% of Cumulative Target` = (!!last_qtr_column/`Cumulative Target`*100)
    ) %>%

    mutate(`% of Cumulative Target*` = percent(`% of Cumulative Target`/100, accuracy = 1)) %>%
    rowwise() %>% 
  mutate(color_bars = case_when(
         `% of Cumulative Target` < yellow_green_entered_employment &
      `% of Cumulative Target` > red_yellow_entered_employment & is_6_30_qtr == 1 & previous_year_target_met == 0 ~ "#FF9B9B",
    `% of Cumulative Target` >= yellow_green_entered_employment ~ "#70AD47",
    `% of Cumulative Target` < yellow_green_entered_employment &
      `% of Cumulative Target` > red_yellow_entered_employment ~ "#FFFF00",
    `% of Cumulative Target` <= red_yellow_entered_employment ~ "#FF9B9B",
    TRUE ~ "lightgray"
  )) |> 
     select(
      `Grantee Name`,
      `% of Cumulative Target`,
      `% of Cumulative Target*`,
      color_bars
    ) %>%
    arrange(desc(`% of Cumulative Target`))
})

renderPlot({

  chart_by_current_target(entered_employment(), "Entered Employment")+
    ylim(NA, max(entered_employment()$`% of Cumulative Target`)*1.2)
  
})

```


Row {.tabset .tabset-fade}
-------------------------------------
### Incumbent Workers Advanced
```{r}
renderPlot({
  
    silly_legend()

    all_grantees$total_iwa +
          scale_x_date(limits = c(as.Date(first_quarter, "%m.%d.%Y"), as.Date(last_quarter, "%m.%d.%Y")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(just_qtrs, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
    })
```

### Progress to Current Year Target
```{r}

incumbent_workers_adv <- reactive({
  
    silly_legend()

    yellow_green_incumbent_workers_adv <- readr::parse_number(t_green()) %>% first()
  red_yellow_incumbent_workers_adv <- readr::parse_number(t_yellow()) %>% first()
  
  master_table_grantees %>%
    filter(`Performance Metric` == "Incumbent Workers Advanced") %>%
    rowwise() %>%
    mutate(
      `Cumulative Target` = sum(c_across(str_replace_all(colnames(targets_viewed), "<br>", "\n"))),
      `% of Cumulative Target` = (!!last_qtr_column/`Cumulative Target`*100)
    ) %>%

    mutate(`% of Cumulative Target*` = percent(`% of Cumulative Target`/100, accuracy = 1)) %>%
    rowwise() %>% 
  mutate(color_bars = case_when(
      `% of Cumulative Target` < yellow_green_incumbent_workers_adv &
      `% of Cumulative Target` > red_yellow_incumbent_workers_adv & is_6_30_qtr == 1 & previous_year_target_met == 0 ~ "#FF9B9B",
    `% of Cumulative Target` >= yellow_green_incumbent_workers_adv ~ "#70AD47",
    `% of Cumulative Target` < yellow_green_incumbent_workers_adv &
      `% of Cumulative Target` > red_yellow_incumbent_workers_adv ~ "#FFFF00",
    `% of Cumulative Target` <= red_yellow_incumbent_workers_adv ~ "#FF9B9B",
    TRUE ~ "lightgray"
  )) |> 
     select(
      `Grantee Name`,
      `% of Cumulative Target`,
      `% of Cumulative Target*`,
      color_bars
    ) %>%
    arrange(desc(`% of Cumulative Target`))
})

renderPlot({
  
    chart_by_current_target(incumbent_workers_adv(), "Incumbent Workers Advanced")+
    ylim(NA, max(incumbent_workers_adv()$`% of Cumulative Target`)*1.2)

})

```




By Grantee
=====================================

Inputs {.sidebar}
-------------------------------------

```{r}
selectInput("grantee", h3("Grantee"), choices = choices, selected = 1)

tags$h3("Reporting Quarters")
selectInput("startdate", "Start Date", choices = df_dates$qtr_end, selected = df_dates_first$qtr_end)
selectInput("enddate", "End Date", choices = df_dates$qtr_end, selected = df_dates_last$qtr_end)

tags$h3("Targets")
sliderInput("targets_by_grantee", "Show Targets for Years:", min = 1, max = 4, value = c(1, 4))



renderText(if (input$startdate == input$enddate) print("Please select different start and end dates.") else print(""))
renderText(if (input$startdate > input$enddate) print("Please select end date that comes after start date.") else print(""))

uiOutput("thebutton")


output$thebutton <- renderUI({
  downloadButton(outputId = "downBtn", label = "Download Grantee Report", style = "width:100%;")
})

# Add download handling
output$downBtn <- downloadHandler(
  filename = "ow_pdf_by_grantee.pdf",
  content = function(file) {
    withProgress(
      message = 'Generating download', 
      style = "notification", 
      value = 0.3, {
    
    params <- list(
      grantee = as.numeric(input$grantee),
      startdate = as.Date(input$startdate, "%Y-%m-%d"),
      enddate = as.Date(input$enddate, "%Y-%m-%d"),
      targets = input$targets_by_grantee,
      thetitle = choices_rev[[as.numeric(input$grantee)]]
    )
    incProgress(0.2)
        
    rendered_report <- rmarkdown::render(
                      input = "ow_pdf_by_grantee.Rmd", 
                      output_format = "pdf_document",
                      output_file = "ow_pdf_by_grantee.pdf",
                      params = params,
                      envir = new.env(parent = globalenv())
                      )
    incProgress(0.4)
    file.copy(rendered_report, file)})
  }
)





renderUI({

  by_grantee_listener()
  
  # THRESHOLDS LEGEND ------------------------
  htmltools::tagList(
    tags$div(class = "legend",
             # fa_i(name = "fas fa-window-restore", id = "dimmer"),
             tags$span(id = "legend-label", "Quarterly Thresholds Key"),
             tags$table(id = "legendid",
               tags$tr(
                 # tags$th(),
                 tags$th(colspan = 2, paste0(current_threshold_by_grantee$quarter, " Quarterly Threshold"))
               ),
               tags$tr(
                 tags$td(
                   div(id = "lightgreen")
                 ),
                 tags$td(class = "legendtext",
                         paste0(current_threshold_by_grantee$nice_green_b, " or above")
                 )
               ),
               tags$tr(
                 tags$td(
                   div(id = "yellow")
                 ),
                 tags$td(class = "legendtext",
                         paste0("Between ", current_threshold_by_grantee$nice_yellow_b, " to ", current_threshold_by_grantee$nice_yellow_t)
                 )
               ),
               tags$tr(
                 tags$td(
                   div(id = "lightpink")
                 ),
                 tags$td(class = "legendtext",
                         paste0(current_threshold_by_grantee$nice_red_t, " or below")
                 )
               )
             )
    )
  )

})


```
 
Row {data-height=575}
------------------------------------

### Summary
```{r}


renderUI({
  
  by_grantee_listener()
  
    # VALUES FOR TABLES -------------------------------
  t_green_by_grantee <- seq(current_threshold_by_grantee$green_b, current_threshold_by_grantee$green_t, by = .01) %>% percent(accuracy = 1)
  t_yellow_by_grantee <- seq(current_threshold_by_grantee$yellow_b, current_threshold_by_grantee$yellow_t, by = .01) %>% percent(accuracy = 1)
  t_red_by_grantee <- seq(0, current_threshold_by_grantee$red_t, by = .01) %>% percent(accuracy = 1)
  
HTML(
    better_by_grantee_table %>% 
      select(-is_6_30_qtr, -previous_year_target_met) |> 
      kbl() |> 
    kable_paper() %>% 
    kable_styling(bootstrap_options = c("striped", "hover"), 
                  position = "left", 
                  full_width = FALSE) %>% 
      column_spec(1, width_min = '140px', width_max = '200px') %>%
      column_spec(
        totalcols, 
        width_min = '70px', 
        width_max = '75px',
        background = case_when(
          better_by_grantee_table$`% of Cumulative Target` %in% t_yellow_by_grantee & better_by_grantee_table$is_6_30_qtr == 1 & better_by_grantee_table$previous_year_target_met == 0 ~ "lightpink",
          better_by_grantee_table$`% of Cumulative Target` %in% t_green_by_grantee ~ "lightgreen",
          better_by_grantee_table$`% of Cumulative Target` %in% t_yellow_by_grantee ~ "yellow",
          better_by_grantee_table$`% of Cumulative Target` %in% t_red_by_grantee ~ "lightpink",
          TRUE ~ "white"),
        extra_css = "border-radius: 4px;") %>%
      scroll_box(width = "900px", height = "100%") |> 
      add_header_above(c(" " = 1, 
                       "Reporting Quarters" = as.numeric(qtr_count), 
                       "Targets" = as.numeric(targets_count),
                       "Progress to Targets" = 4)) %>% 
      add_header_above(c(setNames(as.numeric(totalcols + 2), headername))
  ))
})
```
::: {.footnote}
*% of Current Year Target calculated as most recently available quarterly data divided by sum of cumulative milestones-to-date. e.g. Year 2 milestone is sum of Year 1 & Year 2 annual milestones.
:::
 
 
Row
-------------------------------------

### Total Participants Served
```{r message=FALSE, warning=FALSE}
renderPlot({
  plotnum <- as.numeric(input$grantee)
    charts_tps_ps[[plotnum]] +
      scale_x_date(limits = c(as.Date(input$startdate, "%Y-%m-%d"), as.Date(input$enddate, "%Y-%m-%d")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(quarters_selected, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
})
```

Row
-------------------------------------

### Began Training
```{r}
renderPlot({
  plotnum <- as.numeric(input$grantee)
    charts_train_bt[[plotnum]] +
      scale_x_date(limits = c(as.Date(input$startdate, "%Y-%m-%d"), as.Date(input$enddate, "%Y-%m-%d")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(quarters_selected, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
})
```

Row
-------------------------------------

### Completed Training
```{r}
renderPlot({
  plotnum <- as.numeric(input$grantee)
    charts_train_ct[[plotnum]] +
      scale_x_date(limits = c(as.Date(input$startdate, "%Y-%m-%d"), as.Date(input$enddate, "%Y-%m-%d")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(quarters_selected, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
})
```
 
Row
-------------------------------------


### Completed with Credential
```{r}
renderPlot({
  plotnum <- as.numeric(input$grantee)
    charts_train_cred_coc[[plotnum]] +
      scale_x_date(limits = c(as.Date(input$startdate, "%Y-%m-%d"), as.Date(input$enddate, "%Y-%m-%d")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(quarters_selected, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
})
```

Row
-------------------------------------
### Entered Employment
```{r}
renderPlot({
  plotnum <- as.numeric(input$grantee)
    charts_empl_ee[[plotnum]] +
      scale_x_date(limits = c(as.Date(input$startdate, "%Y-%m-%d"), as.Date(input$enddate, "%Y-%m-%d")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(quarters_selected, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
})
```

Row
-------------------------------------
### Incumbent Workers Advanced
```{r}
renderPlot({
  plotnum <- as.numeric(input$grantee)
    charts_total_iwa[[plotnum]] +
      scale_x_date(limits = c(as.Date(input$startdate, "%Y-%m-%d"), as.Date(input$enddate, "%Y-%m-%d")),
                   date_labels = "%m.%d.%Y",
                   breaks = as.Date(quarters_selected, "%m.%d.%Y"),
                 expand = expansion(mult = 0.2))+
    ggpubr::rotate_x_text(angle = 45) +
    theme(
      axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1)
    )
})
```



All Data
=====================================

Inputs {.sidebar data-width=300}
-------------------------------------


```{r}

grantees <- unique(master_table_grantees$`Grantee Name`)
grantees_len <- length(grantees)
grantees_input <- setNames(grantees, grantees)
  
selectInput(
  "grantees_select", 
  "Grantee:",
  choices = grantees,
  selected = grantees,
  # width = "400px",
  selectize = FALSE,
  size = 10,
  multiple = TRUE
  )
  

# metric_input <- setNames(ps_columns_fctr$renamed, ps_columns_fctr$ow_variable)

metric_input <- setNames(ps_columns_fctr$renamed, ps_columns_fctr$ow_variable)

selectInput(
  "metric_interactive", 
  "Performance Metric:",
  choices = metric_input,
  selected = metric_input,
  width = "300px",
  selectize = FALSE,
  size = 6,
  multiple = TRUE)




```

Row  {data-height=500}
-------------------------------------
### Chart

```{r}
all_data_table <- df %>%
    select(qtr_end, grantee, all_of(ps_cols)) %>%
    mutate(across(all_of(ps_cols), ~replace(., is.na(.), 0))) %>%
    group_by(qtr_end, grantee) %>%
    summarise(across(all_of(ps_cols), sum)) %>%
    pivot_longer(cols = all_of(ps_cols), names_to = "Variable Name", values_to = "Value") %>%
    mutate(qtr_end = as.Date(qtr_end, "%m.%d.%Y")) %>%
    arrange(qtr_end) %>%
    mutate(`Performance Metric` = str_replace_all(`Variable Name`, setNames(df_variables$ow_variable, df_variables$renamed_variables_lower)),
           qtr_end = format(qtr_end, "%m.%d.%Y")) %>%
    pivot_wider(id_cols = c(grantee, `Variable Name`, `Performance Metric`),
                names_from = qtr_end,
                values_from = c(`Value`)) %>%
    rename(`Grantee Name` = grantee)

renderPlot({
  all_data_table %>%
    pivot_longer(cols = all_of(matches("^[0-9]")),
                 names_to = "qtr_end",
                 values_to = "value") %>%
    filter(`Grantee Name` %in% input$grantees_select) %>%
    filter(`Variable Name` %in% input$metric_interactive) %>%
    group_by(`Variable Name`, `Performance Metric`, qtr_end) %>% 
    summarise(value = sum(value)) %>% 
      ungroup() %>% 
    ggplot(aes(x=mdy(qtr_end), y=value, group=`Variable Name`)) +
    geom_line(aes(color = `Performance Metric`), linewidth = 1.5)+
    geom_point(aes(color = `Performance Metric`), size = 4) + 
    ggrepel::geom_label_repel(
      aes(
        label = prettyNum(value, big.mark = ',')),
               inherit.aes = TRUE,
               size = 5) +
    scale_x_date(date_labels = "%m.%d.%Y",
                 breaks = mdy(unique(df$qtr_end)),
                 expand = expansion(mult = 0.2)) +
    scale_y_continuous(expand = expansion(mult = c(0.1, .3))) +
    labs(
      title = "All Grantees",
      # subtitle = subtitle,
      x = "Quarter End",
      y = "Participants") + 
    theme_minimal(base_size = 14) +
    theme(text = element_text(size = 12),
          legend.position = "top",
          legend.text = element_text(size = 12),
          legend.direction = "vertical",
          legend.box = "horizontal", 
          legend.title = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor = element_blank(),
          axis.text.x = element_text(family = "sans",
                                     size = 12,
                                     hjust = .5,
                                     vjust = 1),
          axis.text.y = element_text(size = 12)) +
        guides(color = guide_legend(nrow = 3, byrow = TRUE))+
    ggpubr::rotate_x_text(angle = 45)
})
```




Row  {data-height=400}
-------------------------------------
### Data

```{r}


renderUI({
  HTML(
    all_data_table %>% 
      filter(`Grantee Name` %in% input$grantees_select) %>%
      filter(`Variable Name` %in% input$metric_interactive) %>%
      select(-`Variable Name`) %>%
      kbl_table() %>% 
      scroll_box(height = "350px")
  )
})

```

Row  {data-height=400}
-------------------------------------
### Data Totals

```{r}
renderUI({
  HTML(
    all_data_table %>% 
      filter(`Grantee Name` %in% input$grantees_select) %>%
      filter(`Variable Name` %in% input$metric_interactive) %>%
      group_by(`Variable Name`, `Performance Metric`) %>% 
      summarise(across(matches("^[0-9]"), sum)) %>%
      mutate(`Grantee Name` = "Totals for Grantees Currently Selected in Menu", .before = `Variable Name`) %>%
      mutate(`Variable Name` = factor(`Variable Name`, levels = ps_cols_fctr$renamed)) %>% 
      arrange(`Variable Name`) %>%
      ungroup() %>% 
      select(-`Variable Name`) %>%
      kbl_table() %>% 
      scroll_box(height = "350px")
  )
})
```



Row  {data-height=400}
-------------------------------------
### Targets

```{r}

cols_abbr <- tibble(renamed = ps_cols) %>% 
  cbind(short_target_fctr)

all_targets_table <- df_targets %>% 
    pivot_longer(
      cols = starts_with("target"),
      names_prefix = "target_",
      names_to = c("year", "metric"),
      names_sep = "_",
      values_to = "target"
      ) %>%
    mutate(target = replace(target, is.na(target), 0)) %>%
    select(-grant_number) %>%
    pivot_wider(
      id_cols = c(grantee, metric),
      names_from = "year",
      names_prefix = "03.31.",
      values_from = c("target"),
      values_fn = max
    ) %>%
    rename_with(., ~ str_c(.x, " Target"), .cols = !c(1, 2)) %>%
  mutate(
    metric = str_replace_all(metric, setNames(ps_cols_fctr$renamed, ps_cols_fctr$short))) %>%
  left_join(x = ., y = df_variables, by = c("metric" = "renamed_variables_lower")) %>%
  select(
    `Grantee Name` = grantee,
    `Variable Name` = metric,
    `Performance Metric` = ow_variable,
    everything()
  ) %>%
  select(1:7)

renderUI({
  HTML(
    all_targets_table %>% 
      filter(`Grantee Name` %in% input$grantees_select) %>%
      filter(`Variable Name` %in% input$metric_interactive) %>% 
      select(-c(`Variable Name`)) %>%
      kbl_table() %>% 
      scroll_box(height = "350px")
  )
})

```

Row  {data-height=400}
-------------------------------------
### Targets Totals
```{r}
renderUI({
  HTML(
    all_targets_table %>% 
      filter(`Grantee Name` %in% input$grantees_select) %>%
      filter(`Variable Name` %in% input$metric_interactive) %>%
      group_by(`Variable Name`, `Performance Metric`) %>% 
      summarise(across(matches("^[0-9]"), sum)) %>%
      mutate(`Grantee Name` = "Totals for Grantees Currently Selected in Menu", .before = `Variable Name`) %>% 
      mutate(`Variable Name` = factor(`Variable Name`, levels = ps_cols_fctr$renamed)) %>% 
      arrange(`Variable Name`) %>% 
      ungroup() %>% 
      select(-c(`Variable Name`)) %>%
      kbl_table() %>% 
      scroll_box(height = "350px")
  )
})
```


